A Comparative Quality Metric for Untargeted Fuzzing with Logic State Coverage

### 2024-06-02 paper/main.tex
checkpt

In theory, relative completeness can be naively measured by counting distinctive
program behaviors. However, this naive approach is infeasible as fuzzing
produces hundreds of arbitrarily long instruction streams \emph{every second}.
%
In this section, we propose \emph{logic state coverage} as a proxy of relative
completeness that indirectly counts interesting program behaviors.

>>>>

In theory, interesting behaviors can be naively counted by investigating
every program behavior. However, this naive approach is infeasible as
fuzzing produces hundreds of arbitrarily long instruction streams \emph{every
second}.
%
In this section, we propose \emph{logic state coverage} as an indirect proxy of
counting interesting behaviors.
